% Choose one to switch between slides and handout
\documentclass[]{beamer}
%\documentclass[handout]{beamer}

% Video Meta Data
\title{Smart Contracts and Decentralized Finance}
\subtitle{Blind Bidding}
\author{Prof. Dr. Fabian Schär}
\institute{University of Basel}

% Config File
\input{../config/config.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\thispagestyle{empty}
\begin{frame}[noframenumbering]
	\titlepage
\end{frame}

%%%
\begin{frame}{Submitting a bid}

	\begin{itemize}
		\item Input: A hashed blinded bid
		\item Create a new Bid object
		\item Add the new bid to the sender's list of bids
	\end{itemize}
	
	function bid(bytes32 blindedBid) external payable {
  		Bid memory newBid = Bid({
    	blindedBid: blindedBid,
    	deposit: msg.value
  	});

  		bids[msg.sender].push(newBid);
	}

\end{frame}
%%%	

%%%
\begin{frame}{Data Location}
	\begin{itemize}
		\item Notice when creating a new Bid object we need to specify a location for the object.
		\item All structs and arrays (including strings) can exist in three different locations:
		\begin{itemize}
			\item $memory$: The object is not written or read from the blockchain and only exists in the current scope.
			\item $calldata$: Similar to memory, but can only be used for function arguments in external calls and it is non-modifiable.
			\item $storage$: Loaded from or written onto the blockchain. These are expensive operations, avoid whenever possible.
		\end{itemize}		
		\item Good heuristic: Use calldata for function arguments of external functions. Use storage if you want to load or modify a state variable. Use memory otherwise.
	\end{itemize}

\end{frame}
%%%

%%%
\begin{frame}{The reveal mechanic}
	Let's think about what the reveal function needs to do:
	\begin{itemize}
		\item Accept a list of unencrypted bids to reveal
		\item Validate that the length of this list corresponds to the number of committed bids
		\item Check if the reveal period is active
		\item Ignore fake bids
		\item Update the highest bid and highest bidder if applicable
		\item Handle all refunds
	\end{itemize}

\end{frame}
%%%

%%%
\begin{frame}{Split the function}

	For better readability, we split the logic into two parts:
	\begin{itemize}
		\item reveal() handles all the reveal related checks and refunds
		\item placeBid() handles the bid related checks and refunds
	\end{itemize}
	
	placeBid() is similar to the simple auction's bid function:
	
	function placeBid(address bidder, uint bidAmount) internal returns (bool success) {
  if (bidAmount <= highestBid) {
    return false;
  }
  if (highestBidder != address(0)) {
    // Refund the previously highest bidder.
    pendingReturns[highestBidder] += highestBid;
  }
  highestBid = bidAmount;
  highestBidder = bidder;
  return true;
}

\begin{itemize}
	\item The function is internal, meaning it can only be called from the contract itself.
	\item It returns true if the new highest bid was accepted and false otherwise
\end{itemize} 

\end{frame}
%%%

%%%
\begin{frame}{Simple Reveal}
	Start with a simple version: Only one bid exists

	function reveal(uint bidAmount, bool isLegit, string calldata salt) external {
    bytes32 hashedInput = generateBlindedBid(bidAmount, isLegit, salt);
    Bid storage bidToCheck = bids[msg.sender][0]; // Load the first element of the array
    uint refund;

    if (bidToCheck.blindedBid == hashedInput) {
        // Bid is successfully revealed
        refund = bidToCheck.deposit;
        if (isLegit && bidToCheck.deposit >= bidAmount) {
            // Bid is valid
            bool success = placeBid(msg.sender, bidAmount);
            if(success) {
                // Bid is new highest bid
                refund -= bidAmount;
            }
        }
        // Prevent re-claiming the same deposit
      	bidToCheck.blindedBid = bytes32(0);
    }

    if (refund > 0) {
        payable(msg.sender).transfer(refund);
    }
}
	
\end{frame}
%%%

%%%
\begin{frame}{Loops}
	\begin{itemize}
		\item We need to iterate over all bids of a user
		\item Solidity supports most of the control structures known from similar languages such as JavaScript with the usual semantics.
		\item for-loops are typically used to iterate over arrays:
		\item javascript
			// T[]  array;
			for (uint i = 0; i < array.length; i++) {
			 	T  element = array[i];
			}
		\item continue will skip to the next iteration. break will end the loop.
		\item In addition to for-loops, do and while loops are also available.
	\end{itemize}

	
\end{frame}
%%%

%%%
\begin{frame}{Custom Modifiers}
	\begin{itemize}
		\item The only thing remaining is to end the auction and to implement time constraints
		\item We could do the time constraints similar to the simple auction contract
		\item However, if we have the same repeated require checks at the start (or end) of functions we can make use of custom modifiers
		\item Custom modifiers are a convenient, reusable way to validate inputs to functions
	\end{itemize}
	
	modifier onlyBefore(uint time) {
    require(block.timestamp < time, 'too late');
    _;
}

modifier onlyAfter(uint time) {
    require(block.timestamp > time, 'too early');
    _;
}	
\end{frame}
%%%

%%%
\begin{frame}{Finish the Contract}
	Add a function to end the auction with the modifier onlyAfter:

	function auctionEnd() external onlyAfter(revealEnd) {
  require(!hasEnded, 'Auction already ended');
  emit AuctionEnded(highestBidder, highestBid);
  hasEnded = true;
  payable(beneficiary).transfer(highestBid);
}
\end{frame}
%%%

%%%
\begin{frame}{Excercise}
	Excercise: Add time constraints to bid() and reveal()
\end{frame}
%%%

\end{document}