% Choose one to switch between slides and handout
\documentclass[]{beamer}
%\documentclass[handout]{beamer}

% Video Meta Data
\title{Smart Contracts and Decentralized Finance}
\subtitle{Functions and Modifiers}
\author{Prof. Dr. Fabian Schär}
\institute{University of Basel}

% Config File
\input{../config/config.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\thispagestyle{empty}
\begin{frame}[noframenumbering]
	\titlepage
\end{frame}
%%%

%%%
\begin{frame}{Functions}
	\textbf{Functions are executable parts of a smart contract.}
		
	\uncover<2->{
		\begin{samplecode}{Function Example}
			\input{../assets/solidity_code/function_example.tex}
		\end{samplecode}
	}
	
	\scriptsize
	\begin{columns}[T]
		\begin{column}{0.48\textwidth}
		
		\uncover<3->{
			\texttt{<functionName>}\\
			\begin{itemize}
				\item Pick and set a unique name for your function	
			\end{itemize}
		}
		
		\uncover<4->{
			\texttt{<parameters>}\\
			\begin{itemize}
				\item Used in the \texttt{<function body>}
				\item Must be different from state variables	
			\end{itemize}
		}
		
		\end{column}
		\begin{column}{0.48\textwidth}
		
		\uncover<5->{
			\texttt{<modifiers>}\\
			\begin{itemize}
				\item Accessibility modifiers
				\item State permission modifiers
				\item Special modifiers
				\item Custom modifiers	
			\end{itemize}
		}
		
		\uncover<6->{
			\texttt{<return variables>}
			\begin{itemize}
				\item Optional
				\item Multiple return variables possible	
			\end{itemize}
		}

		\end{column}
	\end{columns}
\end{frame}
%%%

%%%
\begin{frame}{Accessibility Modifiers}
	\textbf{Accessibility modifiers state which accounts can access a function or variable.}
	
	\begin{itemize}
		\item<2-> They are explicitly required for all functions.
		\item<2-> They can be defined for variables, but default to \genkey{private} if omitted. 
	\end{itemize}
	
	\uncover<3->{
	\textbf{Who can access which functions/variables?}
		\begin{table}
			\begin{tabular}{lp{1.6cm}p{1.6cm}p{1.6cm}p{1.6cm}}
			\hline
				\rowcolor{highlight}
				\textbf{Keyword} & \textbf{EOA} & \textbf{This contract} & \textbf{Inheriting contract} & \textbf{External contract}\\
				\genkey{private} & No & Yes & No & No \\
				\genkey{internal} & No & Yes & Yes & No \\
				\genkey{external} & Yes & No & No & Yes \\
				\genkey{public} & Yes & Yes & Yes & Yes \\
				\hline
			\end{tabular}
		\end{table}
	}
	
	\uncover<4->{
	\begin{keytakeaway}{Additional information}
		\begin{itemize}
			\item \genkey{external} can only be used for functions.
			\item Declaring a variable as \genkey{public} will create a getter function with the same name.
			\item \genkey{private} does not mean the variable is invisible.
		\end{itemize}
	\end{keytakeaway}
	}
\end{frame}
%%%

%%%
\begin{frame}{State Permission Modifiers}
	\textbf{State permission modifiers define which functions can read from or modify (write to) the state.}
	\uncover<2->{
		\begin{table}
			\begin{tabular}{lll}
				\hline
				\rowcolor{highlight}
				\textbf{Keyword} & \textbf{Read} & \textbf{Write}\\
				\genkey{pure} & No & No\\
				\genkey{view} & Yes & No\\
				\textit{$<$omitted$>$} & Yes & Yes\\
				\hline
			\end{tabular}
		\end{table}
	}
\end{frame}
%%%

%%%
\begin{frame}{Special and Custom Modifiers}
\textbf{Special modifiers for functions:}
	\begin{itemize}
		\item<1-> \genkey{payable}: allows a function to receive ETH as part of the transaction.
		\item<2-> \genkey{virtual} \& \genkey{override}: used for inheritance (\textcolor{focus}{more on inheritance later!}).
		\item<3-> \genkey{constant} \& \genkey{immutable}: disallow changing the value of a variable during the contract's lifetime.
		\begin{itemize}
			\item<3->{Difference: \genkey{immutable} can be set during contract deployment}	
		\end{itemize}
		\item<4-> Custom (user-defined) modifiers (\textcolor{focus}{more on this later!})
	\end{itemize}
\end{frame}
%%%

%%%
\begin{frame}{Update of the Auction Contract}
	\begin{exercise}{Exercise:}
		\begin{enumerate}
			\item Make sure the variables \texttt{beneficiary}, \texttt{highestBid}, \texttt{highestBidder} and \texttt{hasEnded} are \genkey{public}.
			\item Create a function that allows any EOA or external contract to set the \texttt{beneficiary}.
			\item Self-check: how can you get the values of the previous variables?
		\end{enumerate}
	\end{exercise}
\end{frame}
%%%

%%%
\begin{frame}{Update the Auction Contract}
	\begin{samplecode}{Solution}
		\input{../assets/solidity_code/public_variables.tex}
	\end{samplecode}
\end{frame}
%%%

%%%
\begin{frame}{Contract Constructors}

	\textbf{The \genkey{constructor} is a special function that is executed when the contract is deployed.}
	
	\begin{samplecode}{Constructor Example}
			\input{../assets/solidity_code/constructor_example.tex}
	\end{samplecode}
	
\end{frame}

\begin{frame}{Immutable \texttt{beneficiary}}

	\begin{exercise}{Exercise:}
		\begin{enumerate}
			\item Remove \genkey{function} \texttt{initialize(}\typesunits{address}\texttt{\_beneficiary)} \genkey{external} \texttt{\{\dots\}} from the auction contract.
			\item Use the \genkey{constructor} to set the \texttt{beneficiary} at the time of contract deployment for the contract's entire lifetime.
		\end{enumerate}
	\end{exercise}
		
	\uncover<2->{
	\textbf{Solution:}
	\begin{samplecode}{Constructor for the Auction Contract}
			\input{../assets/solidity_code/constructor_beneficiary.tex}
	\end{samplecode}
	
	\begin{samplecode}{Line \ref{line:benef} in the previous contract}
		address public immutable beneficiary;
	\end{samplecode}
	}
	
\end{frame}
%%%

%%%
\begin{frame}{Current State of the Auction Contract}
	\begin{samplecode}{After Integrating the Constructor into \texttt{SimpleAuction}}
		\input{../assets/solidity_code/constructor.tex}
	\end{samplecode}
\end{frame}
%%%

\end{document}